### 2025-05-09 sec/authoring-workflow.tex
[refactory] created util.fld and moved insertion sort into it
[update] first changes on the paper

@@

\section{Results}
\label{sec:results}

\subsection{Success Rate by Testcase}
\label{subsec:success_rate_by_test_case}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.95\linewidth]{fig/success_rate_by_test_case}
    \caption{Success rate by testcases}\label{fig:success_rate_by_test_case}
\end{figure}

>>>>

\subsection{Paragraph with generated expression}
Figure \ref{fig:fluid-example-paragraph} shows the Fluid code of a Paragraph with Fluid expression generated by the authoring assistant.
Figure \ref{fig:fluid-scigen} shows the Fluid code written for the scigen datasets and examples.
\begin{figure}[h]
    \small
    {\lstinputlisting[language=Fluid]{website/authoring-assistant/fluid/1805.02474v1-10.fld}}
    \vspace{-0.5em}
    \caption{Fluid source code example Paragraph}
    \label{fig:fluid-example-paragraph}
\end{figure}

\begin{figure}[h]
    \small
    {\lstinputlisting[language=Fluid]{fluid-common/scigen.fld}}
    \vspace{-0.5em}
    \caption{Fluid library written for scigen}
    \label{fig:fluid-scigen}
\end{figure}

@@

### 2025-05-09 sec/introduction.tex
[update] first changes on the paper

\begin{figure}[h]
   \includegraphics[width=0.9\textwidth]{fig/ipcc-mockup.png}
   \caption{Mockup of end-user transparency features (numbered 1 to 8)}
   \label{fig:ipcc-mockup}
\end{figure}

@@

\subsubsection{Use cases}
Two potential scenarios for this sort of technology:

@@

NLP aspect of the problem is potentially a big problem space in itself. We will restrict interest to certain
idiomatic uses of natural language in making/justifying scientific claims. Examples:

\begin{itemize}
\item quantitative expressions
\begin{itemize}
   \item pure numerical values
   \item percentages
   \item rounded or normalised numbers
\end{itemize}
\item aggregation
\begin{itemize}
   \item average
   \item totals
   \item count
\end{itemize}
\item trends
\begin{itemize}
   \item comparisons
   \item ranks
\end{itemize}
\item graded Adjectives (e.g.~\emph{virtually certain}, \emph{exceptionally unlikely})
\item references to visual elements and their parts (mereology)
\end{itemize}

\begin{table}[!ht]
   \centering
   \tiny
   \begin{tabular}{p{2cm}p{1.3cm}p{6.7cm}p{2cm}}
      \toprule
      Type & Category & Example & Status \\
      \midrule
      pure numerical values & Quantitative expressions & (findWithKey' "model" "LSTM" tableData).time\_s & Done \\
      percentages & Quantitative expressions &  "The Energy Sector accounts for total methane emissions of", (record.emissions / sum(map (fun x -> x.emissions) (getByYear year tableData))) * 100 & Done \\
      rounded or normalised numbers & Quantitative expressions & ~ & ~ \\
      average & Aggregation & "The average methane emissions for the year 2024 is", (sumEmissions year tableData / length records) & Done \\
      totals & Aggregation & "The total methane emissions for the year 2024 is", (sumEmissions year tableData) & Done \\
      count & Aggregation & ~ & ~ \\
      comparisons & Trends & trendWord (findWithKey' "model" "BiLSTM" tableData).time\_s (findWithKey' "model" "LSTM" tableData).time\_s "growing from" "shrinking to" "equal to" & Done \\
      ranks & Trends & let pos = findIndex "model" "CNN" (insertionSort cmpTime tableData) in rankLabel "lowest" pos & Done \\
      Graded adjectives  & Adjectives & ~ & ~ \\
      References to visual elements and their parts (mereology) & ~ & ~ & ~ \\
      \bottomrule
   \end{tabular}
\end{table}

>>>>

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig/scigen-mr-1906.02780-10.png}
    \caption{Website example with the generated expression from authoring assistant}\label{fig:scigen-example-website}
\end{figure}

\subsection{Use cases}
Two potential scenarios for this sort of technology:

@@

NLP aspect of the problem is potentially a big problem space in itself. We will restrict interest to certain
idiomatic uses of natural language in making/justifying scientific claims.
Examples \ref{tab:fluid_examples}

\begin{table}[!ht]
    \centering
    \footnotesize
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{>{\raggedright\arraybackslash}p{2cm} >{\raggedright\arraybackslash}p{5cm} >{\raggedright\arraybackslash}p{6cm}}
        \toprule
        \textbf{Type}                & \textbf{Example} & \textbf{Generated Expression} \\
        \midrule
        \multicolumn{3}{>{\raggedright\arraybackslash}c}{\textbf{Quantitative expressions.}} \\
        \midrule
        Numerical value
        & BiLSTM gives significantly better accuracies compared to uni-directional LSTM2, with the training time per epoch growing from \hl{67} seconds to 106 seconds. &
        \begin{lstlisting}[language=Fluid,numbers=none]
(findWithKey' "model" "LSTM" tableData).time\_s
        \end{lstlisting} \\
        Percentage &
        The Energy Sector accounts for total methane emissions of \hl{52.80\%} in 2030. &
        \begin{lstlisting}[language=Fluid,numbers=none]
(record.emissions / sum(map (fun x -> x.emissions) (getByYear year tableData))) * 100
        \end{lstlisting}  \\
        Rounded or normalised number & ~                & ~                             \\
        \multicolumn{3}{>{\raggedright\arraybackslash}c}{\textbf{Aggregation.}} \\
        \midrule
        Average
        & The average methane emissions for the year 2030 is \hl{13.51} &
        \begin{lstlisting}[language=Fluid,numbers=none]
(sumEmissions year tableData / length records)
        \end{lstlisting} \\
        Min                          & ~                & ~                             \\
        Max                          & ~                & ~                             \\\
        Ranks &
        On the other hand, a 3-layer stacked CNN gives an accuracy of 81.46\%, which is also the \hl{lowest} compared with BiLSTM, hierarchical attention and S-LSTM  &
        \begin{lstlisting}[language=Fluid,numbers=none]
let pos = findIndex "model" "CNN" (insertionSort cmpTime tableData) in rankLabel "lowest" pos
        \end{lstlisting} \\
        Total &
        The total methane emissions for the year 2030 is \hl{37.74} for Agriculture &
        \begin{lstlisting}[language=Fluid,numbers=none]
sumEmissions year tableData
        \end{lstlisting} \\
        *Count                       & ~                & ~                             \\
        \multicolumn{3}{>{\raggedright\arraybackslash}c}{\textbf{Trends \& Adjectives.}} \\
        \midrule
        Comparisons
        & BiLSTM gives significantly better accuracies compared to uni-directional LSTM2, with the training time per epoch \hl{growing from} 67 seconds to 106 seconds. &
        \begin{lstlisting}[language=Fluid,numbers=none]
trendWord (findWithKey' "model" "BiLSTM" tableData).time\_s (findWithKey' "model" "LSTM" tableData).time\_s "growing from" "shrinking to" "equal to"
        \end{lstlisting} \\
        *Graded adjective            & ~                & ~                             \\
        *Reference to visual element                            & ~                & ~                             \\
        \bottomrule
    \end{tabular}
    \caption{Example expressions generated by the Authoring Assistant, classified by type. In green, the expression is already tested.}
    \label{tab:fluid_examples}
    \renewcommand{\arraystretch}{1.0}
\end{table}
